Machine-learned embedded atom method

### 2019-12-12 doc/papers/ml-eam/manuscript.tex
The manuscript is updated.

\documentclass[prb,reprint]{revtex4-2}

@@

\author{Xin Chen, 
        Li-Fang Wang, 
        Xing-Yu Gao,
        Ya-Fan Zhao,
        De-Ye Lin$^\mathrm{*}$, 
        Wei-Dong Chu,
        Hai-Feng Song$^\mathrm{*}$}

\affiliation{
    Institute of Applied Physics and Computational Math, 
    Beijing 100088, China}

\affiliation{
    CAEP Software Center for High Performance Numerical Simulation, 
    Beijing 100088, China}

@@

The Rose constraint incoporates the universal equation of state (Rose et al) 
into the total loss function. The Mishin-modified equation 
\begin{equation}
\label{eq:rose_eos}
E(x) = E_{0}\left[
    1 + \alpha x + \beta \alpha^3 x^3 \frac{2x + 3}{(x - 1)^2} \right]
    e^{-\alpha x}
\end{equation}
is used because the original form tends to underestimate energies under high 
pressures. In Equation \ref{eq:rose_eos}, $E_{0}$ is the energy of the 
equilibrium structure, $x = a / a_{0} - 1$ is the relative isotropic scaling 
factor ($a$ is the lattice constant), $\beta$ is a chosen parameter and 
\begin{equation}
\label{eq:rose_alpha}
\alpha = \sqrt{-\frac{9 V_{0} B }{E_{0}}}
\end{equation}
where $V_0$ is the equilibrium volume and $B$ is the bulk modulus. The adoption
of the Rose constraint guarantees the exact predictions of bulk modulus and 
the energy-volume curve. The loss of the Rose EOS constraint 
$\mathbf{L}^{\mathrm{Rose}}$  is measured as the 2-norm of the energy 
differences between $E(x)^{\mathrm{dft}}$ and their corresponding predicted 
$E(x)$: 
\begin{equation}
\label{eq:rose_loss}
\mathbf{L}^{\mathrm{Rose}} = \sum_{\Omega}{
    \sqrt{\sum_{i}{\left(E(x_i) - E(x_i)^{\mathrm{dft}}\right)^2}}
}
\end{equation}
Here $\Omega$ denotes all selected crystals. In this work, for each included 
crystal, we use the same choices of $x$: 
$x_{i} = x_{0} + \Delta x \cdot i, x_{0} = -0.1, N_{t}^{\mathrm{max}} = 20, 
\Delta x=0.01$. In this work, $\beta^{\mathrm{Ni}}$ is 0.005 and 
$\beta^{\mathrm{Mo}}$ is 0.150.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Ni - Material Properties
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}
\centering
\begin{tabular}{lccccc}
\hline
                              & DFT  & SNAP \cite{SNAP} & EAM              & ML-EAM         & Exp.                           \\
\hline
$T_{m}$(K)                    &      & 1785             & 1520 \cite{ZJW2} & 1520           & 1728                           \\
$c_{11}$ (GPa)                & 276  & 276 (0.0\%)      & 248 (-10.1\%)    & 274 (-0.7\%)   & 261 \cite{Ni_Elastic_Exp}      \\
$c_{12}$ (GPa)                & 159  & 159 (0.0\%)      & 147 (-7.5\%)     & 163 (2.5\%)    & 151 \cite{Ni_Elastic_Exp}      \\
$c_{44}$ (GPa)                & 132  & 132 (0.0\%)      & 125 (-5.3\%)     & 131 (-0.8\%)   & 132 \cite{Ni_Elastic_Exp}      \\
$B_{\mathrm{VRH}}$ (GPa)      & 198  & 198 (0.0\%)      & 181 (-8.6\%)     & 195 (0.0\%)    & 188                            \\
$G_{\mathrm{VRH}}$ (GPa)      & 95   & 95 (0.0\%)       & 87 (-8.4\%)      & 93 (-2.1\%)    & 93                             \\
$\mu$                         & 0.29 & 0.29 (0.0\%)     & 0.29 (0.0\%)     & 0.29 (0.0\%)   & 0.29                           \\
$E_{v}$ (eV)                  & 1.46 & 1.68 (15.1\%)    & 1.68 (15.1\%)    & 1.71 (17.1\%)  & 1.54–1.80 \cite{Ni_EvEmEa_Exp} \\
$E_{m}$ (eV)                  & 1.12 & 1.07 (-4.5\%)    & 0.90 (-19.6\%)   & 0.87 (-22.3\%) & 1.01–1.48 \cite{Ni_EvEmEa_Exp} \\
$E_{a} = E_{v} + E_{m} $ (eV) & 2.58 & 2.75 (6.6\%)     & 2.58 (0.0\%)     & 2.58 (0.0\%)   & 2.77–2.95 \cite{Ni_EvEmEa_Exp} \\
\hline
\end{tabular}
\caption{\label{table:Ni_properties} Comparison of the calculated and 
experimental material properties of elementary fcc Ni. $T_{m}$ is the melting 
point. $c_{ij}$ represents elastic constants. $E_{v}$ and $E_{m}$ are vacancy 
formation energy and migration energy, respectively. SNAP refers to the 
elementary Ni SNAP model.
}
\end{table*}

@@

For the Mo dataset, the situation is quite different. The original Zjw04 has 
extremely large MAEs: the energy \textbf{rMAE} is $\sim 98$ meV/atom and the 
force MAE is more than 0.40 eV/\AA. Our method can significantly reduce the 
error: ML-EAM can achieve test MAEs of 21.9 meV/atom and 0.28 eV/\AA and overall
MAEs of 28.1 meV/atom and 0.32 eV/\AA. We also optimized an ADP potential for 
this dataset. Interestingly, ML-ADP achieves almost exactly the same MAEs with 
ML-EAM: 22.1 meV/atom and 0.27 eV\AA on the test set and 27.9 meV/atom and 0.33 
eV/\AA on the entire dataset. On the contrast, the SNAP method (13.2 meV/atom, 
0.25 eV/\AA) behaves better. But considering the computational cost, the 
optimized EAM and ADP are totally accepetable.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Mo - Material Properties
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}
\centering
\begin{tabular}{lcccccc}
\hline
                              & DFT  & SNAP \cite{SNAP_Mo} & EAM \cite{ZJW2} & ML-EAM         & ML-ADP         & Exp.                      \\
\hline
$T_{m}$(K)                    &      & 3000                & 3750            & 2940           & 2880           & 2890                      \\
$c_{11}$ (GPa)                & 472  & 473 (0.2\%)         & 457 (-3.2\%)    & 472 (0.0\%)    & 473 (0.2\%)    & 479 \cite{Mo_Elastic_Exp} \\
$c_{12}$ (GPa)                & 158  & 152 (-3.8\%)        & 168 (6.3\%)     & 158 (0.0\%)    & 160 (1.2\%)    & 165 \cite{Mo_Elastic_Exp} \\
$c_{44}$ (GPa)                & 106  & 107 (0.9\%)         & 116 (9.4\%)     & 106 (0.0\%)    & 105 (-0.9\%)   & 108 \cite{Mo_Elastic_Exp} \\
$B_{\mathrm{VRH}}$ (GPa)      & 263  & 259 (-1.5\%)        & 264 (0.4\%)     & 262 (-0.4\%)   & 264 (0.4\%)    & 270 \cite{Mo_Elastic_Exp} \\
$G_{\mathrm{VRH}}$ (GPa)      & 124  & 126 (1.6\%)         & 127 (2.4\%)     & 125 (0.8\%)    & 124 (0.0\%)    & 125 \cite{Mo_Elastic_Exp} \\
$\mu$                         & 0.30 & 0.29 (-3.3\%)       & 0.29 (-3.3\%)   & 0.30 (0.9\%)   & 0.30 (0.0\%)   & 0.30                      \\
$E_{v}$ (eV)                  & 2.87 & 2.61 (-9.1\%)       & 3.02 (5.2\%)    & 1.99 (-30.7\%) & 2.01 (-30.0\%) &                           \\
$E_{m}$ (eV)                  & 1.12 & 1.39 (24.1\%)       & 1.54 (37.5\%)   & 1.33 (18.7\%)  & 1.27 (13.4\%)  &                           \\
$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%)       & 4.56 (14.3\%)   & 3.32 (-16.8\%) & 3.28 (-17.8\%) & 4.00 \cite{Mo_Ea_Exp}     \\
\hline
\end{tabular}
\caption{\label{table:Mo_properties} Comparison of the calculated and 
experimental material properties of elementary bcc Mo. SNAP refers to the 
elementary SNAP Mo model.
}
\end{table*}

@@

Table \ref{table:Ni_properties} and \ref{table:Mo_properties} summerize the 
predicted material properties of fcc Ni and bcc Mo, including the melting point 
$T_{m}$, the elastic constants ($c_{11}$, $c_{12}$ and $c_{44}$), the vacancy 
formation energy $E_{v}$, the migration energy $E_{m}$ and the activation energy 
$E_{a}$. The original Zjw04 potentials were developed by fitting material 
properties so they already perform well on these metrics. Our ML-EAM and ML-ADP 
not only inherit this feature but also gain significant improvement on 
predicting elastic constants: the relative errors of the elastic constants as 
well as the Voigt-Reuss-Hill bulk modulus, shear modulus and homogeneous 
Poisson's ratio, for both bcc Mo and fcc Ni, are reduced from $\sim$10\% to 
0-2\%.

We further examined our ML-EAM and ML-ADP by calculating the melting temperature
of fcc Ni and bcc Mo using the solid-liquid coexistence approach. For fcc Ni, 
$30 \times 10 \times 10$ supercells were used and for bcc the supercells were 
$30 \times 15 \times 15$. The time step was set to 1 fs. The simulation for each 
temperature was carried out for at least 300 ps. For fcc Ni, $T_{m}$ remains the 
same for ML-EAM, 200 K lower than the experiment $T_m$. However, the calculated 
$T_{m}$ of Mo is greatly improved. The original Zjw04 $T_{m}$ is around 3750 K, 
800 K higher than experiment (2890 K). Both ML-EAM and ML-ADP can give very 
accurate melting temperature.

@@

In fact, both the EAM and the SNAP formalisms can be considered as variants of 
MBE truncated at $k=2$. For the EAM method, the embedding contribution $F(\rho)$ 
serves as the one-body term and the overall pairwise contribution 
$\frac{1}{2}\sum_{j\ne i}{\phi(r_{ij})}$ is just a plain transcription of the 
two-body term in Equation \ref{eq:MBE_atomic}. The ADP formalism, which 
introduces extra pairwise dipole and quadrupole interactions, does not change
this nature. For the SNAP method, the atomic energy is calculated with the 
following equation: 
\begin{equation}
\label{eq:snap_formalism}
E_i = \beta_{0}^{\alpha_{i}} + \sum_{k}{\beta_{k}^{\alpha_{i}}B_{k}^i}
\end{equation} 
where $\beta_{0}^{\alpha_i}$ and $\beta_{k}^{\alpha_i}$ are learnable scalar
parameters, $\alpha_i$ indicates the element type of atom $i$. $B_{k}^{i}$ is a 
bispectrum coefficient. The calculation of $B_{k}^{i}$ is very complicated but 
it is still a two-body term. The overall two-body contribution is a linear 
combination of $B_{k}^{i}$. Thus, the SNAP formalism can be viewed as an 
assemble of a simplified one-body term with a complicated two-body term. On the 
other hand, the EAM formalism is built up with a 'complicated' one-body term and 
a rather simple two-body term. Hence, for the fcc and bcc systems, both methods 
perform similarly.

As we analysed in Section \ref{sec:transformation}, the fundamental atomic 
descriptor of EAM, the $N \times N^{\mathrm{nl}} \times 4$ matrix $\mathbf{G}$, 
is composed of just raw interatomic distances. However, interatomic distances
alone may not uniquely describe a structure. To avoid this problem, the cutoff 
was raised up to 6.5 \AA. As a comparison, the overall $r_{cut}$ is 4.6 \AA for 
the binary SNAP. But such descriptor is still too rough to describe complicated 
potential energy surfaces (e.g. bcc Mo). To further enhance EAM/ADP, perhaps we 
shall consider adding real three-body terms (e.g. Tersoff).

>>>>

\documentclass[prb,reprint,superscriptaddress]{revtex4-2}

@@

\author{Xin Chen}
\affiliation{
    Institute of Applied Physics and Computational Math, 
    Beijing 100088, China}

\author{Li-Fang Wang}
\affiliation{
    Institute of Applied Physics and Computational Math, 
    Beijing 100088, China}

\author{Xing-Yu Gao}
\affiliation{
    Institute of Applied Physics and Computational Math, 
    Beijing 100088, China}

\author{Ya-Fan Zhao}
\affiliation{
    CAEP Software Center for High Performance Numerical Simulation, 
    Beijing 100088, China}
\affiliation{
    Institute of Applied Physics and Computational Math, 
    Beijing 100088, China}

\author{De-Ye Lin}
\email{lindeye0716@163.com}
\affiliation{
    CAEP Software Center for High Performance Numerical Simulation, 
    Beijing 100088, China}
\affiliation{
    Institute of Applied Physics and Computational Math, 
    Beijing 100088, China}

\author{Wei-Dong Chu}
\affiliation{
    Institute of Applied Physics and Computational Math, 
    Beijing 100088, China}

\author{Hai-Feng Song}
\email{song_haifeng@iapcm.ac.cn}
\affiliation{
    Institute of Applied Physics and Computational Math, 
    Beijing 100088, China}
\affiliation{
    CAEP Software Center for High Performance Numerical Simulation, 
    Beijing 100088, China}

@@

The Rose constraint incoporates the universal equation of state (Rose et al) 
into the total loss function. The Mishin-modified equation 
\begin{equation}
\label{eq:rose_eos}
E(x) = E_{0}\left[
    1 + \alpha x + \beta \alpha^3 x^3 \frac{2x + 3}{(x - 1)^2} \right]
    e^{-\alpha x}
\end{equation}
is used because the original form tends to underestimate energies under high 
pressures. In Equation \ref{eq:rose_eos}, $E_{0}$ is the energy of the 
equilibrium structure, $x = a / a_{0} - 1$ is the relative isotropic scaling 
factor ($a$ is the lattice constant), $\beta$ is a chosen parameter and 
\begin{equation}
\label{eq:rose_alpha}
\alpha = \sqrt{-\frac{9 V_{0} B }{E_{0}}}
\end{equation}
where $V_0$ is the equilibrium volume and $B$ is the bulk modulus. The adoption
of the Rose constraint guarantees the exact predictions of bulk modulus and 
the energy-volume curve. The loss of the Rose EOS constraint 
$\mathbf{L}^{\mathrm{Rose}}$  is measured as the 2-norm of the energy 
differences between $E(x)^{\mathrm{dft}}$ and their corresponding predicted 
$E(x)$: 
\begin{equation}
\label{eq:rose_loss}
\mathbf{L}^{\mathrm{Rose}} = \sum_{\Omega}{
    \sqrt{\sum_{i}{\left(E(x_i) - E(x_i)^{\mathrm{dft}}\right)^2}}
}
\end{equation}
Here $\Omega$ denotes all selected crystals. In this work, for each included 
crystal, we use the same choices of $x$: 
$x_{i} = x_{0} + \Delta x \cdot i, x_{0} = -0.1, N_{t}^{\mathrm{max}} = 20, 
\Delta x=0.01$. In this work, $\beta^{\mathrm{Ni}}$ is 0.005 and 
$\beta^{\mathrm{Mo}}$ is 0.008.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Ni - Material Properties
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}
\centering
\begin{tabular}{lccccc}
\hline
                              & DFT  & SNAP \cite{SNAP} & EAM              & ML-EAM         & Exp.                           \\
\hline
$T_{m}$(K)                    &      & 1785             & 1520 \cite{ZJW2} & 1520           & 1728                           \\
$c_{11}$ (GPa)                & 276  & 276 (0.0\%)      & 248 (-10.1\%)    & 274 (-0.7\%)   & 261 \cite{Ni_Elastic_Exp}      \\
$c_{12}$ (GPa)                & 159  & 159 (0.0\%)      & 147 (-7.5\%)     & 163 (2.5\%)    & 151 \cite{Ni_Elastic_Exp}      \\
$c_{44}$ (GPa)                & 132  & 132 (0.0\%)      & 125 (-5.3\%)     & 131 (-0.8\%)   & 132 \cite{Ni_Elastic_Exp}      \\
$B_{\mathrm{VRH}}$ (GPa)      & 198  & 198 (0.0\%)      & 181 (-8.6\%)     & 195 (-1.5\%)    & 188                           \\
$G_{\mathrm{VRH}}$ (GPa)      & 95   & 95 (0.0\%)       & 87 (-8.4\%)      & 93 (-2.1\%)    & 93                             \\
$\mu$                         & 0.29 & 0.29 (0.0\%)     & 0.29 (0.0\%)     & 0.29 (0.0\%)   & 0.29                           \\
$E_{v}$ (eV)                  & 1.46 & 1.68 (15.1\%)    & 1.68 (15.1\%)    & 1.71 (17.1\%)  & 1.54–1.80 \cite{Ni_EvEmEa_Exp} \\
$E_{m}$ (eV)                  & 1.12 & 1.07 (-4.5\%)    & 0.90 (-19.6\%)   & 0.87 (-22.3\%) & 1.01–1.48 \cite{Ni_EvEmEa_Exp} \\
$E_{a} = E_{v} + E_{m} $ (eV) & 2.58 & 2.75 (6.6\%)     & 2.58 (0.0\%)     & 2.58 (0.0\%)   & 2.77–2.95 \cite{Ni_EvEmEa_Exp} \\
\hline
\end{tabular}
\caption{\label{table:Ni_properties} Comparison of the calculated and 
experimental material properties of elementary fcc Ni. $T_{m}$ is the melting 
point. $c_{ij}$ represents elastic constants. $E_{v}$ and $E_{m}$ are vacancy 
formation energy and migration energy, respectively. SNAP refers to the 
elementary Ni SNAP model.
}
\end{table*}

@@

For the Mo dataset, the situation is quite different. The original Zjw04 has 
extremely large MAEs: the energy \textbf{rMAE} is $\sim 98$ meV/atom and the 
force MAE is more than 0.40 eV/\AA. Our method can significantly reduce the 
error: ML-EAM can achieve test MAEs of 23.8 meV/atom and 0.26 eV/\AA and overall
MAEs of 26.7 meV/atom and 0.30 eV/\AA. We also optimized an ADP potential for 
this dataset. Interestingly, ML-ADP gets better results: 20.6 meV/atom and 
0.24 eV\AA on the test set and 18.7 meV/atom and 0.29 eV/\AA on the entire 
dataset. On the contrast, the SNAP method (13.2 meV/atom, 0.25 eV/\AA) behaves 
slightly better than ML-ADP. But considering the computational cost, the 
ML-ADP is totally acceptable.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Mo - Material Properties
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}
\centering
\begin{tabular}{lcccccc}
\hline
                              & DFT  & SNAP \cite{SNAP_Mo} & EAM \cite{ZJW2} & ML-EAM         & ML-ADP         & Exp.                      \\
\hline
$T_{m}$(K)                    &      & 3000                & 3750            & 2840           & 2910           & 2890                      \\
$c_{11}$ (GPa)                & 472  & 473 (0.2\%)         & 457 (-3.2\%)    & 463 (-1.9\%)   & 469 (-0.6\%)   & 479 \cite{Mo_Elastic_Exp} \\
$c_{12}$ (GPa)                & 158  & 152 (-3.8\%)        & 168 (6.3\%)     & 153 (-3.2\%)   & 159 (0.6\%)    & 165 \cite{Mo_Elastic_Exp} \\
$c_{44}$ (GPa)                & 106  & 107 (0.9\%)         & 116 (9.4\%)     & 98 (-7.5\%)    & 102 (-3.8\%)   & 108 \cite{Mo_Elastic_Exp} \\
$B_{\mathrm{VRH}}$ (GPa)      & 263  & 259 (-1.5\%)        & 264 (0.4\%)     & 256 (-2.7\%)   & 262 (-0.4\%)   & 270 \cite{Mo_Elastic_Exp} \\
$G_{\mathrm{VRH}}$ (GPa)      & 124  & 126 (1.6\%)         & 127 (2.4\%)     & 118 (-4.8\%)   & 121 (-2.4\%)   & 125 \cite{Mo_Elastic_Exp} \\
$\mu$                         & 0.30 & 0.29 (-3.3\%)       & 0.29 (-3.3\%)   & 0.30 (0.0\%)   & 0.30 (0.0\%)   & 0.30                      \\
$E_{v}$ (eV)                  & 2.87 & 2.61 (-9.1\%)       & 3.02 (5.2\%)    & 1.96 (-31.7\%) & 2.51 (-12.5\%) &                           \\
$E_{m}$ (eV)                  & 1.12 & 1.39 (24.1\%)       & 1.54 (37.5\%)   & 1.33 (18.7\%)  & 1.06 (-5.3\%)  &                           \\
$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%)       & 4.56 (14.3\%)   & 3.29 (-17.5\%) & 3.57 (-10.5\%) & 4.00 \cite{Mo_Ea_Exp}     \\
\hline
\end{tabular}
\caption{\label{table:Mo_properties} Comparison of the calculated and 
experimental material properties of elementary bcc Mo. SNAP refers to the 
elementary SNAP Mo model.
}
\end{table*}

@@

Table \ref{table:Ni_properties} and \ref{table:Mo_properties} summerize the 
predicted material properties of fcc Ni and bcc Mo, including the melting point 
$T_{m}$, the elastic constants ($c_{11}$, $c_{12}$ and $c_{44}$), the vacancy 
formation energy $E_{v}$, the migration energy $E_{m}$ and the activation energy 
$E_{a}$. The original Zjw04 potentials were developed by fitting material 
properties so they already perform well on these metrics. For the fcc Ni, the 
machine-learned EAM has gained better performances on predicting elastic 
constants. For the bcc Mo, ML-ADP not only gives quality predictions on elastic 
properties but also significantly reduces the error of predicting $E_m$. We also 
tested these models with surface energy, as shown in Fig 
\ref{fig:surface_energy}. One must note that all the slab structures are relaxed 
independently with corresponding potentials. For the fcc Ni, ML-EAM can give 
almost exactly the same results with DFT. For the more complicated bcc Mo, the 
central-force ML-EAM model becomes not that good due to the directional d 
bonding \cite{ADP0}. The angular correction, introduced by Mishin, shows 
its importance. ML-ADP can give acceptable results, just like the SNAP method.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: Surface Energy - Plot
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}
\centering
\includegraphics[scale=0.4]{figures/surface_energy.png}
\caption{\label{fig:surface_energy} Comparison of calculated surface energies of 
\textbf{(a)} fcc Ni and \textbf{(b)} bcc Mo.}
\end{figure}

We further examined our ML-EAM and ML-ADP by calculating the melting temperature
of fcc Ni and bcc Mo using the solid-liquid coexistence approach. For fcc Ni, 
$30 \times 10 \times 10$ supercells were used and for bcc the supercells were 
$30 \times 15 \times 15$. The time step was set to 1 fs. The simulation for each 
temperature was carried out for at least 300 ps. For fcc Ni, $T_{m}$ remains the 
same for ML-EAM, 200 K lower than the experiment $T_m$. However, the calculated 
$T_{m}$ of Mo is greatly improved. The original Zjw04 $T_{m}$ is around 3750 K, 
800 K higher than experiment (2890 K) while both ML-EAM and ML-ADP can give 
quite accurate melting temperature.

@@

In fact, both the EAM and the SNAP formalisms can be considered as variants of 
MBE truncated at $k=2$. For the EAM method, the embedding contribution $F(\rho)$ 
serves as the one-body term and the overall pairwise contribution 
$\frac{1}{2}\sum_{j\ne i}{\phi(r_{ij})}$ is just a plain transcription of the 
two-body term in Equation \ref{eq:MBE_atomic}. For the SNAP method, the atomic 
energy is calculated with the following equation: 
\begin{equation}
\label{eq:snap_formalism}
E_i = \beta_{0}^{\alpha_{i}} + \sum_{k}{\beta_{k}^{\alpha_{i}}B_{k}^i}
\end{equation} 
where $\beta_{0}^{\alpha_i}$ and $\beta_{k}^{\alpha_i}$ are learnable scalar
parameters, $\alpha_i$ indicates the element type of atom $i$. $B_{k}^{i}$ is a 
bispectrum coefficient. The calculation of $B_{k}^{i}$ is very complicated but 
it is still a two-body term. The overall two-body contribution is a linear 
combination of $B_{k}^{i}$. Thus, the SNAP formalism can be viewed as an 
assemble of a simplified one-body term with a complicated two-body term. On the 
other hand, the EAM formalism is built up with a 'complicated' one-body term and 
a rather simple two-body term. The central-force EAM works well on fcc metals. 
For bcc metals with partially filled d bands, the directional d bonding cannot
be ignored. Hence, the pairwise dipole and quadrupole functions introduced by 
ADP are necessary.

As we analysed in Section \ref{sec:transformation}, the fundamental atomic 
descriptor of EAM, the $N \times N^{\mathrm{nl}} \times 4$ matrix $\mathbf{G}$, 
is composed of just raw interatomic distances. However, interatomic distances
alone may not uniquely describe a structure. To avoid this problem, the cutoff 
was raised up to 6.5 \AA. As a comparison, the overall $r_{cut}$ is 4.6 \AA for 
the binary SNAP. But such descriptor is still too rough to describe complicated 
potential energy surfaces (e.g. bcc Mo). To further enhance EAM/ADP, complicated
three--atoms interactions may be necessary.
